Fusing Filters with Integer Linear Programming

### 2014-05-16 2014betterfusionforfilters/section/05-Benchmarks.tex
quickhull

\subsection{QuickHull}
One benchmark we did not implement, but is worth mentioning, is QuickHull.
The core of the QuickHull algorithm is shown below.
Given a line and an array of points, the points are filtered to those above the line,
and the farthest point above the line is also found.

\begin{code}

hull :: (Point,Point) -> Array Point -> Array Point
hull line@(l,r) pts
 = let pts' = filter (above   line) pts
       ma   = fold   (maxFrom line) pts'
   in (hull (l, ma) pts') ++ (hull (ma, r) pts')
\end{code}

>>>>

\subsection{QuickHull}
QuickHull is another program that is worth mentioning, as it highlights some fusion opportunities with filters.
The core of the QuickHull algorithm is shown below: given a line and an array of points, the points are filtered to those above the line, and the farthest point above the line is also found.

\begin{code}
hull :: (Point,Point) -> Array Point -> Array Point
hull line@(l,r) pts
 = let pts' = filter (above   line) pts
       ma   = fold   (maxFrom line) pts'
   in (hull (l, ma) pts') ++ (hull (ma, r) pts')
\end{code}
